Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-06 workflow/workflow.Rmd
correspondance of clsuters

Cluster name | Description | Color | Correspondence
-------------|-------------|-------| ----------
c1 | HBC | blue | original 1, 5
c2 | GBC | green | original 2, 3, 11
c3 | mSUS | red | original 4, 7
c4 | mOSN | orange | original 9, 12
c5 | Immature Neuron | purple | original 10, 14
c6 | MV | brown | original 15

@@

```{r}
our_cl <- primaryClusterNamed(ceObj)
cl = our_cl[our_cl != "-1"]
pal = pal[names(pal) != "-1"]
X <- W[our_cl != "-1", ]
mds <- cmdscale(dist(X), eig = TRUE, k = 4)
X <- mds$points

lineages <- getLineages(X, clusterLabels = cl, start.clus = "c1")
```

@@

```{r tree, fig.cap="Slingshot: Cells color-coded by cluster in a 4-dimensional MDS space with connecting lines between cluster centers representing the inferred global lineage structure."}
pairs(lineages, type="lineages", col = pal[cl])
```

@@

```{r curves, fig.cap="Slingshot: Cells color-coded by cluster in a 4-dimensional MDS space with smooth curves representing each inferred lineage."}
lineages <- getCurves(lineages)

pairs(lineages, type="curves", col = pal[cl])
```

```{r lineages}
lineages
```

@@

```{r slingshotsupervised, eval=FALSE}
lineages <- getLineages(X, clusterLabels = cl, start.clus = "c1",
                         end.clus = c("c3", "c6"))
lineagees <- getCurves(lineages)
pairs(lineages, type="curves", col = pal[primaryClusterNamed(ceObj)])
pairs(lineages, type="lineages", col = pal[primaryClusterNamed(ceObj)], show.constraints = TRUE)

@@

```{r fitgam}
t <- pseudotime(lineages)[,1]
y <- assays(se)$normalizedValues[, our_cl != "-1"]
gam.pval <- apply(y,1,function(z){
  d <- data.frame(z=z, t=t)
  tmp <- gam(z ~ lo(t), data=d)
  p <- summary(tmp)[4][[1]][1,5]
  p
})
```

>>>>

Cluster name | Description | Color | Correspondence
-------------|-------------|-------| ----------
c1 | HBC | blue | original 1, 5
c2 | GBC | green | original 2, 3, 11
c3 | mSUS | red | original 4, 7
c4 | im | orange | -2 
c5 | mOSN | purple | original 9, 12
c6 | Immature Neuron | brown | original 10, 14
c7 | MV | cian | original 15

@@

```{r}
our_cl <- primaryClusterNamed(ceObj)
cl = our_cl[!our_cl %in% c("-1", "c4")]
pal = pal[!names(pal) %in% c("-1", "c4")]
X <- W[!our_cl %in% c("-1", "c4"), ]
mds <- cmdscale(dist(X), eig = TRUE, k = 4)
X <- mds$points

lineages <- getLineages(X, clusterLabels = cl, start.clus = "c1")
print(lineages)
```

@@

```{r tree, fig.cap="Slingshot: Cells color-coded by cluster in a 4-dimensional MDS space with connecting lines between cluster centers representing the inferred global lineage structure."}
pairs(lineages, type="lineages", col = pal[cl])
print(lineages)
```

@@

```{r curves, fig.cap="Slingshot: Cells color-coded by cluster in a 4-dimensional MDS space with smooth curves representing each inferred lineage."}
lineages <- getCurves(lineages)
pairs(lineages, type="curves", col = pal[cl])
print(lineages)
```

```{r lineages}
lineages
print(lineages)
```

@@

```{r slingshotsupervised, eval=FALSE}
lineages <- getLineages(X, clusterLabels = cl, start.clus = "c1",
                         end.clus = c("c3", "c7"))
lineagees <- getCurves(lineages)
pairs(lineages, type="curves", col = pal[primaryClusterNamed(ceObj)])
pairs(lineages, type="lineages", col = pal[primaryClusterNamed(ceObj)], show.constraints = TRUE)

@@

```{r fitgam}
print(lineages)
t <- pseudotime(lineages)[,1]
y <- assays(se)$normalizedValues[, !our_cl %in% c("-1", "c4")]
gam.pval <- apply(y,1,function(z){
  d <- data.frame(z=z, t=t)
  tmp <- gam(z ~ lo(t), data=d)
  p <- summary(tmp)[4][[1]][1,5]
  p
})
```
